---
title: "Creating enriched heatmaps"
author: "Spiro Stilianoudakis"
date: "4/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages and functions

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)

source("Z:/TAD_data_analysis/functions_for_R_package/preciseTAD.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADRF.R")
source("Z:/TAD_data_analysis/functions_for_R_package/TADrfe.R")
source("Z:/TAD_data_analysis/functions_for_R_package/distance_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/percent_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/count_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/binary_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/signal_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/annots_to_granges_func.R")
source("Z:/TAD_data_analysis/functions_for_R_package/extract_boundaries_func.R")

```

## Enriched heatmap function 

```{r}
enriched_func <- function(boundaries, annotations, e=5, w=50, ct){
  axis_names <- c(paste0("-",e,"kb"), "Center", paste0(e,"kb"))
  
  norm_mat <- normalizeToMatrix(annotations, 
                                boundaries, 
                                value_column = "coverage", 
                                extend = e*1000, 
                                w = 50,
                                mean_mode = "w0",
                                keep = c(0,.999))
  EH <- EnrichedHeatmap(norm_mat, 
                        col = ifelse(ct=="ARROWHEAD" | ct=="PEAKACHU" | ct=="LOLLIPOP", c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)),
                                     c("black",colorRampPalette(c("white", "pink", "red"))(99))), 
                        #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                        row_title="Boundaries",
                        show_heatmap_legend = FALSE,
                        row_title_side="left", 
                        column_title=ct, 
                        axis_name = axis_names,
                        column_title_gp = gpar(fontsize = 10),
                        row_title_gp = gpar(fontsize = 10),
                        axis_name_gp = gpar(fontsize = 10),height=unit(2, "in"),
                        width=unit(2, "in")
                        top_annotation = HeatmapAnnotation(height=unit(2, "in"),
                                                           width=unit(2, "in"),
                                                           lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
                                                                                           fontsize = 10,
                                                                                           lwd = 2), 
                                                                                 axis_param = list(side = "right",
                                                                                                   facing = "inside"))))
  return(EH)
}

```


## ARROWHEAD

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```


###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```


###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```


###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```


###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```


###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```


###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="ARROWHEAD")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```


## PEAKACHU

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```


###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```


###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```


###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```


###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```


###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```


###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="PEAKACHU")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```


## LOLLIPOP

### GM12878

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```


###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```


###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```


###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```

### K562

#### Create granges from top tfbs

```{r}
genomicElements.GR <- annots_to_granges_func(filepath = "Z:/TAD_data_analysis/annotations/all_common_annotations/k562/topTFBS",
                                             pattern="*.bed",
											 signal=4)
```

#### Extracting called and predicted boundaries

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #

```

###### CTCF

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[1]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[1]], e=5, w=50, ct="preciseTAD")
```


###### RAD21

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[2]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[2]], e=5, w=50, ct="preciseTAD")
```


###### SMC3

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[3]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[3]], e=5, w=50, ct="preciseTAD")
```


###### ZNF143

```{r}
enriched_func(all_pred_bounds, genomicElements.GR[[4]], e=5, w=50, ct="LOLLIPOP")
enriched_func(all_true_bounds, genomicElements.GR[[4]], e=5, w=50, ct="preciseTAD")
```


########################################3

# Plotting

```{r}

pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #


e=5
norm_mat_pt_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_ctcf <- colSums(norm_mat_pt_ctcf[])
norm_mat_pt_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_rad21 <- colSums(norm_mat_pt_rad21[])
norm_mat_pt_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_smc3 <- colSums(norm_mat_pt_smc3[])
norm_mat_pt_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_znf143 <- colSums(norm_mat_pt_znf143[])



norm_mat_a_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_ctcf <- colSums(norm_mat_a_ctcf[])
norm_mat_a_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_rad21 <- colSums(norm_mat_a_rad21[])
norm_mat_a_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_smc3 <- colSums(norm_mat_a_smc3[])
norm_mat_a_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_a_znf143 <- colSums(norm_mat_a_znf143[])


df <- data.frame(X = rep(c(1:200),8),
                 E = c(norm_mat_pt_ctcf,
                       norm_mat_pt_rad21,
                       norm_mat_pt_smc3,
                       norm_mat_pt_znf143,
                       norm_mat_a_ctcf,
                       norm_mat_a_rad21,
                       norm_mat_a_smc3,
                       norm_mat_a_znf143),
                 Tool = c(rep("preciseTAD", 200*4),
                          rep("Arrowhead", 200*4)),
                 A = rep(c(rep("CTCF", 200),
                       rep("RAD21", 200),
                       rep("SMC3", 200),
                       rep("ZNF143", 200)),2))

ggplot(data=df, aes(x=X, y=E/5000, group=Tool, color=Tool)) +
  facet_grid(. ~ A) +
  geom_line(alpha=.75, size=1.5) +
  xlab("Distance from boundary (kb)") +
  ylab("") +
  scale_color_manual(name="Tool", 
                       values=c("blue", "forestgreen"))+
  scale_x_continuous(breaks=c(0,100,200),
                     label=c("-5", "Center", "5")) +
  theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 20),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text.x = element_text(size = 20),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=20),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")


################################################################################

pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))
  
  true_bound_list[[i]] <- called_and_pred[[3]]
  pred_bound_list[[i]] <- called_and_pred[[2]]
  
}

all_true_bounds <- do.call("c", true_bound_list)
all_pred_bounds <- do.call("c", pred_bound_list)

length(all_true_bounds) #
length(all_pred_bounds) #


e=10
norm_mat_pt_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_ctcf <- colSums(norm_mat_pt_ctcf[])
norm_mat_pt_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_rad21 <- colSums(norm_mat_pt_rad21[])
norm_mat_pt_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_smc3 <- colSums(norm_mat_pt_smc3[])
norm_mat_pt_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_pred_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_pt_znf143 <- colSums(norm_mat_pt_znf143[])



norm_mat_p_ctcf <- normalizeToMatrix(genomicElements.GR[[1]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_ctcf <- colSums(norm_mat_p_ctcf[])
norm_mat_p_rad21 <- normalizeToMatrix(genomicElements.GR[[2]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_rad21 <- colSums(norm_mat_p_rad21[])
norm_mat_p_smc3 <- normalizeToMatrix(genomicElements.GR[[3]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_smc3 <- colSums(norm_mat_p_smc3[])
norm_mat_p_znf143 <- normalizeToMatrix(genomicElements.GR[[4]], 
                              all_true_bounds, 
                              value_column = "coverage", 
                              extend = e*1000, 
                              w = 50,
                              mean_mode = "coverage")
norm_mat_p_znf143 <- colSums(norm_mat_p_znf143[])


df <- data.frame(X = rep(c(1:400),8),
                 E = c(norm_mat_pt_ctcf,
                       norm_mat_pt_rad21,
                       norm_mat_pt_smc3,
                       norm_mat_pt_znf143,
                       norm_mat_p_ctcf,
                       norm_mat_p_rad21,
                       norm_mat_p_smc3,
                       norm_mat_p_znf143),
                 Tool = c(rep("preciseTAD", 400*4),
                          rep("Peakachu", 400*4)),
                 A = rep(c(rep("CTCF", 400),
                       rep("RAD21", 400),
                       rep("SMC3", 400),
                       rep("ZNF143", 400)),2))


ggplot(data=df, aes(x=X, y=E/10000, group=Tool, color=Tool)) +
    facet_grid(. ~ A) +
    geom_line(alpha=.75, size=1.5) +
    xlab("Distance from boundary (kb)") +
    ylab("") +
    scale_color_manual(name="Tool", 
                       values=c("red", "forestgreen"))+
    scale_x_continuous(breaks=c(0,200,400),
                       label=c("-10", "Center", "10")) +
    theme_minimal() +
    theme_bw()+
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 20),
          axis.title.x = element_text(size = 20),
          axis.title.y = element_text(size = 20),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text.x = element_text(size = 20),
          #panel.spacing = unit(2, "lines"),
          legend.text=element_text(size=20),
          legend.title=element_text(size=20),
          plot.title = element_text(size=20),
          legend.position = "bottom")
```

