---
title: "Exploring Feature Engineering"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Libraries

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

```

#Feature Engineering

## Exploring Correlations

###GM12878

####10kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_10kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_10kb) #4595    4
sigcorrs_gm12878_10kb[,3:4] <- round(sigcorrs_gm12878_10kb[,3:4], 4)
sigcorrs_gm12878_10kb <- sigcorrs_gm12878_10kb[order(sigcorrs_gm12878_10kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_10kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_10kb) #21  4
highcorrs_gm12878_10kb[,3:4] <- round(highcorrs_gm12878_10kb[,3:4], 2)
highcorrs_gm12878_10kb <- highcorrs_gm12878_10kb[order(abs(highcorrs_gm12878_10kb$value), decreasing = TRUE),]


#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_10kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_25kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_25kb) #4683    4
sigcorrs_gm12878_25kb[,3:4] <- round(sigcorrs_gm12878_25kb[,3:4], 4)
sigcorrs_gm12878_25kb <- sigcorrs_gm12878_25kb[order(sigcorrs_gm12878_25kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_25kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_25kb) #50  4
highcorrs_gm12878_25kb[,3:4] <- round(highcorrs_gm12878_25kb[,3:4], 2)
highcorrs_gm12878_25kb <- highcorrs_gm12878_25kb[order(abs(highcorrs_gm12878_25kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_25kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_50kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_50kb) #
sigcorrs_gm12878_50kb[,3:4] <- round(sigcorrs_gm12878_50kb[,3:4], 4)
sigcorrs_gm12878_50kb <- sigcorrs_gm12878_50kb[order(sigcorrs_gm12878_50kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_50kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_50kb) #
highcorrs_gm12878_50kb[,3:4] <- round(highcorrs_gm12878_50kb[,3:4], 2)
highcorrs_gm12878_50kb <- highcorrs_gm12878_50kb[order(abs(highcorrs_gm12878_50kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_50kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

####100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_gm12878_100kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_gm12878_100kb) #4373    4
sigcorrs_gm12878_100kb[,3:4] <- round(sigcorrs_gm12878_100kb[,3:4], 4)
sigcorrs_gm12878_100kb <- sigcorrs_gm12878_100kb[order(sigcorrs_gm12878_100kb$pvals, decreasing = FALSE),]

highcorrs_gm12878_100kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_gm12878_100kb) #424   4
highcorrs_gm12878_100kb[,3:4] <- round(highcorrs_gm12878_100kb[,3:4], 2)
highcorrs_gm12878_100kb <- highcorrs_gm12878_100kb[order(abs(highcorrs_gm12878_100kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_gm12878_100kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

###K562

####10kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_10kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.0000000000),] #remove main daigonal
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_10kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_10kb) #4595    4
sigcorrs_K562_10kb[,3:4] <- round(sigcorrs_K562_10kb[,3:4], 4)
sigcorrs_K562_10kb <- sigcorrs_K562_10kb[order(sigcorrs_K562_10kb$pvals, decreasing = FALSE),]

highcorrs_K562_10kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_10kb) #21  4
highcorrs_K562_10kb[,3:4] <- round(highcorrs_K562_10kb[,3:4], 2)
highcorrs_K562_10kb <- highcorrs_K562_10kb[order(abs(highcorrs_K562_10kb$value), decreasing = TRUE),]


#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_10kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]


get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_25kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_25kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_25kb) #4683    4
sigcorrs_K562_25kb[,3:4] <- round(sigcorrs_K562_25kb[,3:4], 4)
sigcorrs_K562_25kb <- sigcorrs_K562_25kb[order(sigcorrs_K562_25kb$pvals, decreasing = FALSE),]

highcorrs_K562_25kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_25kb) #50  4
highcorrs_K562_25kb[,3:4] <- round(highcorrs_K562_25kb[,3:4], 2)
highcorrs_K562_25kb <- highcorrs_K562_25kb[order(abs(highcorrs_K562_25kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_25kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5) 
```

####50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]


get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_50kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_50kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_50kb) #
sigcorrs_K562_50kb[,3:4] <- round(sigcorrs_K562_50kb[,3:4], 4)
sigcorrs_K562_50kb <- sigcorrs_K562_50kb[order(sigcorrs_K562_50kb$pvals, decreasing = FALSE),]

highcorrs_K562_50kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_50kb) #
highcorrs_K562_50kb[,3:4] <- round(highcorrs_K562_50kb[,3:4], 2)
highcorrs_K562_50kb <- highcorrs_K562_50kb[order(abs(highcorrs_K562_50kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_50kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

####100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad)
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]


get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cormat)

melted_cormat <- melt(upper_tri, na.rm = TRUE)

reorder_cormat <- function(cormat){
# Use correlation between variables as distance
dd <- as.dist((1-cormat)/2)
hc <- hclust(dd)
cormat <-cormat[hc$order, hc$order]
}

cormat_reorder <- reorder_cormat(cormat)

upper_tri_reorder <- get_upper_tri(cormat_reorder)

melted_cormat_reorder <- melt(upper_tri_reorder, na.rm = TRUE)

corplot_K562_100kb <- ggplot(data = melted_cormat_reorder, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
 ylab("") +
 xlab("") +  
 theme_minimal()+ 
 theme_bw()+
 guides(fill=FALSE)+
 theme(axis.text.x = element_text(angle = 45, vjust = 1, 
    size = 5, hjust = 1),
       axis.text.y = element_text(size = 5))
 #coord_fixed()

pvals <- rcorr(as.matrix(binswtad))$P
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
pvals <- pvals[-which(rownames(pvals) == "Znf274"), -which(colnames(pvals) == "Znf274")]

upper_tri_pvals <- get_upper_tri(pvals) 
melted_pvals <- melt(upper_tri_pvals, na.rm = TRUE)
melted_cormat2 <- melted_cormat[-which(melted_cormat$value==1.00000000),]
melted_cormat2$pvals <- melted_pvals$value

#find significant correlations
sigcorrs_K562_100kb <- melted_cormat2[which(melted_cormat2$pvals<=.05),]
dim(sigcorrs_K562_100kb) #4373    4
sigcorrs_K562_100kb[,3:4] <- round(sigcorrs_K562_100kb[,3:4], 4)
sigcorrs_K562_100kb <- sigcorrs_K562_100kb[order(sigcorrs_K562_100kb$pvals, decreasing = FALSE),]

highcorrs_K562_100kb <- melted_cormat2[which(melted_cormat2$value > 0.70 | melted_cormat2$value < (-0.70)),] 
dim(highcorrs_K562_100kb) #424   4
highcorrs_K562_100kb[,3:4] <- round(highcorrs_K562_100kb[,3:4], 2)
highcorrs_K562_100kb <- highcorrs_K562_100kb[order(abs(highcorrs_K562_100kb$value), decreasing = TRUE),]

#clustered heatmap
my_palette <- colorRampPalette(c("blue", "white", "red"))(n = 299)
clustcorplot_K562_100kb <- heatmap.2(cormat,
          #cellnote = cormat,  # same data set for cell labels
          main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          margins =c(6,6),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #breaks=col_breaks,    # enable color transition at specified limits
          dendrogram="row",     # only draw a row dendrogram
          key=FALSE,
          keysize = 1,
          cexRow = .5,
          cexCol = .5)
```

## Using corrplot function

### GM12878

#### 10kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")


corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


#### 25kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")


corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


#### 50kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")


corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

#### 100kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")


corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

### K562

#### 10kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]


corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


#### 25kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]


corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


#### 50kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]


corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


#### 100kb

```{r}

train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")

binswtad <- train[which(train$y=="Yes"),]
binswtad <- binswtad[,grep("count", names(binswtad))]

names(binswtad) <- gsub(paste(c("K562",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", names(binswtad))


cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]


corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


## Stratifying by annotation group (using pca data--flanked TAD boundaries)

###GM12878

####10kb

##### Counts

```{r}
pcadat_gm12878_10kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_count.rds")

colnames(pcadat_gm12878_10kb_count) <- gsub("_count","",colnames(pcadat_gm12878_10kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_10kb_count_chromstates <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_10kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_chromstates))


cormat <- cor(pcadat_gm12878_10kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_10kb_count_histones <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% histonevars)]

colnames(pcadat_gm12878_10kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_histones))


cormat <- cor(pcadat_gm12878_10kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_10kb_count_tfbs <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_10kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_tfbs))


cormat <- cor(pcadat_gm12878_10kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


##### Percents

```{r}
pcadat_gm12878_10kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_perc.rds")

colnames(pcadat_gm12878_10kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_10kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_10kb_perc_chromstates <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_10kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_chromstates))


cormat <- cor(pcadat_gm12878_10kb_perc_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_10kb_perc_histones <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% histonevars)]

colnames(pcadat_gm12878_10kb_perc_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_histones))


cormat <- cor(pcadat_gm12878_10kb_perc_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_10kb_perc_tfbs <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% tfbsvars)]

colnames(pcadat_gm12878_10kb_perc_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_tfbs))


cormat <- cor(pcadat_gm12878_10kb_perc_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

####Distances

```{r}
pcadat_gm12878_10kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_dist.rds")

colnames(pcadat_gm12878_10kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_10kb_dist))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_10kb_dist_chromstates <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% chromstatevars)]

colnames(pcadat_gm12878_10kb_dist_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_chromstates))


cormat <- cor(pcadat_gm12878_10kb_dist_chromstates, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_10kb_dist_histones <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% histonevars)]

colnames(pcadat_gm12878_10kb_dist_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_histones))


cormat <- cor(pcadat_gm12878_10kb_dist_histones, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_10kb_dist_tfbs <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% tfbsvars)]

colnames(pcadat_gm12878_10kb_dist_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_tfbs))


cormat <- cor(pcadat_gm12878_10kb_dist_tfbs, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

####25kb

##### Counts

```{r}
pcadat_gm12878_25kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_count.rds")

colnames(pcadat_gm12878_25kb_count) <- gsub("_count","",colnames(pcadat_gm12878_25kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_25kb_count_chromstates <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_25kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_chromstates))


cormat <- cor(pcadat_gm12878_25kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_25kb_count_histones <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% histonevars)]

colnames(pcadat_gm12878_25kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_histones))


cormat <- cor(pcadat_gm12878_25kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_25kb_count_tfbs <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_25kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_tfbs))


cormat <- cor(pcadat_gm12878_25kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


##### Percents

```{r}
pcadat_gm12878_25kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_perc.rds")

colnames(pcadat_gm12878_25kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_25kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_25kb_perc_chromstates <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_25kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_chromstates))


cormat <- cor(pcadat_gm12878_25kb_perc_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_25kb_perc_histones <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% histonevars)]

colnames(pcadat_gm12878_25kb_perc_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_histones))


cormat <- cor(pcadat_gm12878_25kb_perc_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_25kb_perc_tfbs <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% tfbsvars)]

colnames(pcadat_gm12878_25kb_perc_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_tfbs))


cormat <- cor(pcadat_gm12878_25kb_perc_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

####Distances

```{r}
pcadat_gm12878_25kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_dist.rds")

colnames(pcadat_gm12878_25kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_25kb_dist))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_25kb_dist_chromstates <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% chromstatevars)]

colnames(pcadat_gm12878_25kb_dist_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_chromstates))


cormat <- cor(pcadat_gm12878_25kb_dist_chromstates, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_25kb_dist_histones <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% histonevars)]

colnames(pcadat_gm12878_25kb_dist_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_histones))


cormat <- cor(pcadat_gm12878_25kb_dist_histones, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_25kb_dist_tfbs <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% tfbsvars)]

colnames(pcadat_gm12878_25kb_dist_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_tfbs))


cormat <- cor(pcadat_gm12878_25kb_dist_tfbs, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

####50kb

##### Counts

```{r}
pcadat_gm12878_50kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_count.rds")

colnames(pcadat_gm12878_50kb_count) <- gsub("_count","",colnames(pcadat_gm12878_50kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_50kb_count_chromstates <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_50kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_chromstates))


cormat <- cor(pcadat_gm12878_50kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_50kb_count_histones <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% histonevars)]

colnames(pcadat_gm12878_50kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_histones))


cormat <- cor(pcadat_gm12878_50kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_50kb_count_tfbs <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_50kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_tfbs))


cormat <- cor(pcadat_gm12878_50kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


##### Percents

```{r}
pcadat_gm12878_50kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_perc.rds")

colnames(pcadat_gm12878_50kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_50kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_50kb_perc_chromstates <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_50kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_chromstates))


cormat <- cor(pcadat_gm12878_50kb_perc_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_50kb_perc_histones <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% histonevars)]

colnames(pcadat_gm12878_50kb_perc_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_histones))


cormat <- cor(pcadat_gm12878_50kb_perc_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_50kb_perc_tfbs <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% tfbsvars)]

colnames(pcadat_gm12878_50kb_perc_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_tfbs))


cormat <- cor(pcadat_gm12878_50kb_perc_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

####Distances

```{r}
pcadat_gm12878_50kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_dist.rds")

colnames(pcadat_gm12878_50kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_50kb_dist))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_50kb_dist_chromstates <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% chromstatevars)]

colnames(pcadat_gm12878_50kb_dist_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_chromstates))


cormat <- cor(pcadat_gm12878_50kb_dist_chromstates, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_50kb_dist_histones <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% histonevars)]

colnames(pcadat_gm12878_50kb_dist_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_histones))


cormat <- cor(pcadat_gm12878_50kb_dist_histones, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_50kb_dist_tfbs <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% tfbsvars)]

colnames(pcadat_gm12878_50kb_dist_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_tfbs))


cormat <- cor(pcadat_gm12878_50kb_dist_tfbs, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

####100kb

##### Counts

```{r}
pcadat_gm12878_100kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_count.rds")

colnames(pcadat_gm12878_100kb_count) <- gsub("_count","",colnames(pcadat_gm12878_100kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_100kb_count_chromstates <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_100kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_chromstates))


cormat <- cor(pcadat_gm12878_100kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_100kb_count_histones <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% histonevars)]

colnames(pcadat_gm12878_100kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_histones))


cormat <- cor(pcadat_gm12878_100kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_100kb_count_tfbs <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_100kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_tfbs))


cormat <- cor(pcadat_gm12878_100kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


##### Percents

```{r}
pcadat_gm12878_100kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_perc.rds")

colnames(pcadat_gm12878_100kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_100kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_100kb_perc_chromstates <- pcadat_gm12878_100kb_perc[,which(colnames(pcadat_gm12878_100kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_100kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_chromstates))


cormat <- cor(pcadat_gm12878_100kb_perc_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_100kb_perc_histones <- pcadat_gm12878_100kb_perc[,which(colnames(pcadat_gm12878_100kb_perc) %in% histonevars)]

colnames(pcadat_gm12878_100kb_perc_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_histones))


cormat <- cor(pcadat_gm12878_100kb_perc_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_100kb_perc_tfbs <- pcadat_gm12878_100kb_perc[,which(colnames(pcadat_gm12878_100kb_perc) %in% tfbsvars)]

colnames(pcadat_gm12878_100kb_perc_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_tfbs))


cormat <- cor(pcadat_gm12878_100kb_perc_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

####Distances

```{r}
pcadat_gm12878_100kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_dist.rds")

colnames(pcadat_gm12878_100kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_100kb_dist))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_100kb_dist_chromstates <- pcadat_gm12878_100kb_dist[,which(colnames(pcadat_gm12878_100kb_dist) %in% chromstatevars)]

colnames(pcadat_gm12878_100kb_dist_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_chromstates))


cormat <- cor(pcadat_gm12878_100kb_dist_chromstates, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_100kb_dist_histones <- pcadat_gm12878_100kb_dist[,which(colnames(pcadat_gm12878_100kb_dist) %in% histonevars)]

colnames(pcadat_gm12878_100kb_dist_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_histones))


cormat <- cor(pcadat_gm12878_100kb_dist_histones, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_100kb_dist_tfbs <- pcadat_gm12878_100kb_dist[,which(colnames(pcadat_gm12878_100kb_dist) %in% tfbsvars)]

colnames(pcadat_gm12878_100kb_dist_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_dist_tfbs))


cormat <- cor(pcadat_gm12878_100kb_dist_tfbs, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

```


#### Saving GM12878 Correlation Plots

```{r}

corfunction <- function(resolution, predictortype, annotation){
  
}

```


